\chapter{Introduction}
\label{ch:intro}
\section{Purpose }
\Large 
The purpose of this Software Requirement Specification (SRS) is:


\section{Intended Audience}
\Large {


}
\section{Intended Use}
\Large 

\section{Product Scope}

\section{Risk Definition}
\Large 



\newpage



% User Story Section
\chapter{Overall Description}
\label{User story}
\section{User Classes and Characteristics}



\section{User Needs}
\Large{

}
\section{Operating Environment}




%The following part done by 380
 \section {Constraints}
 \Large
 


  \section {Assumptions}
\Large
  
\chapter{Requirements}
\label{Requirements}

\section{Functional Requirements}
\Large{

}
\section {Non-Functional Requirements}
\Large{
i. User data including personal preferences and device control history must be securely stored and encrypted.\\ \\
ii. The system should respond to user input or sensor data within a maximum of 1 second.\\ \\
iii. The system should be able to handle peak users load during morning and evening hours without getting slowdowns.\\ \\
iv. Software updates and patches should be easy to apply ensuring the system easy to update.\\ \\
v. The system should be compatible to wide range of devices including smartphone, tablets.\\
vi. It should support concurrent control and monitoring of active devices.\\
vii. The system architecture should allow for easy addition of new devices or sensors without major modifications.\\ \\
viii.It should support expansion to accommodate additional apartments or units in the future.\\ \\
ix. Failures or errors should be handled and system should overcome data loss.\\ \\
x. The system should allow integration third-party services.\\
xi. Access to the system's administrative functions should be protected by strong authentication.\\ \\
xii. Clear user documentation should be provided to assist with set up, configuration and troubleshooting.\\\\
xiii. For any canceled service requested the total bill will be deducted of the service charge.\\\\



}
%THis is SRS Doc.

